Why Donors Donate?

### 2020-09-11 analysis/05_market_simulator.Rmd
Updated posterior draws for public_political_social_charity_demo beta

# Beta's of everything. The only model we care about right now
public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i)

@@

# beta_test <- as.data.frame(matrix(rep(0), nrow = 13))
# 
# beta_test$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
# 
# beta_test$ai_issue <- 0
# beta_test$ai_issue[4] <- 1
# beta_test$ai_issue[8] <- 1
# beta_test$ai_issue[9] <- 1
# 
# 
# beta_test$gp_issue <- 0
# beta_test$gp_issue[4] <- 1
# beta_test$gp_issue[5] <- 1
# beta_test$gp_issue[8] <- 1
# beta_test$gp_issue[9] <- 1
# 
# 
# beta_test$ox_issue <- 0
# beta_test$ox_issue[4] <- 1
# beta_test$ox_issue[6] <- 1
# beta_test$ox_issue[8] <- 1
# beta_test$ox_issue[9] <- 1
# 
# beta_test$rc_issue <- 0
# beta_test$rc_issue[4] <- 1
# beta_test$rc_issue[7] <- 1
# beta_test$rc_issue[8] <- 1
# beta_test$rc_issue[9] <- 1
# 
# 
# 
#   ai_exp_util1 <- round(exp(t(beta_test[, 3]) %*% as.matrix(p_beta1)),2)
#   gp_exp_util1 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta1)),2)
#   ox_exp_util1 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta1)),2)
#   rc_exp_util1 <- round(exp(t(beta_test[, 6]) %*% as.matrix(p_beta1)),2)
# 
#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))

>>>>

# Beta's of everything. The only model we care about right now
public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()

@@
